Very simple spline models

### 2023-01-12 src/pages.Rmd
Added source link to 2020 definition pages

---
title: "Pages written in xxxx template"
source: new
date: "2023-01-10"
categories:
- Blog post
tags:
- Website details
output: html_document
---

@@

```{r}
write_yaml <- function(page_year) {
  date_line <- paste0("date", ": 20", page_year, "-12-31")
  output_text <- glue('
  ---
  title: "Pages written in 20{page_year}"
  source: new
  {date_line}
  categories:
  - Blog post
  tags:
  - Website details
  output: html_document
  ---')
  return(output_text)
}
```

```{r}
write_links <- function(yr_list) {
  glue("[{yr}](http://new.pmean.com/{yr}/)") %>%
    paste(collapse=" | ")
}
```

@@

```{r}
check_dates <- function(file_text) {
  file_text %>%
    str_subset(fixed("date: ")) %>%
    str_remove(fixed("date: ")) %>%
    str_remove_all('"') %>%
    str_remove_all("'")  -> file_date
  if (length(file_date)==0) return("Error: no date")
  if (length(file_date)==0) return("Error: multiple dates")
  return(file_date)
}
```

```{r}
write_list <- function(page_year) {
  # get file list
  list.files(path=glue("../text/{page_year}", pattern="*.md")) %>%
    str_subset("md$") -> f
  # open files and find information
  file_source <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{page_year}/{fn}"))
    # get source
    file_source <- append(
      file_source,
      check_source(file_text))
    #get dates
    date_list <- append(
      date_list,
      check_dates(file_text))
  }
  # strip extensions
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> f
  n <- length(f)
  o <- order(date_list, f)
  # create RMarkdown text
  header <- glue("New website ({n} files)")
  file_list <- glue(
    "+ {date_list[o]} ",
    "[{f[o]}]",
    "(http://new.pmean.com/{f[o]}/)  ") %>%
    paste(collapse="  \n")
  # search for problem files

  return(paste0(header, file_list))
}
```

```{r}
write_yaml(21)
```

`r write_list(21)`

>>>>

---
title: "Pages written in a given year"
source: new
date: "2023-01-10"
categories:
- Blog post
tags:
- Website details
output: html_document
---

@@

```{r}
write_yaml <- function(page_year) {
  date_line <- paste0("date", ": 20", page_year, "-12-31")
  output_text <- glue('
  ---
  title: "Pages written in 20{page_year}"
  source: new
  date: 20{page_year}-12-31
  categories:
  - Blog post
  tags:
  - Website details
  output: html_document
  ---')
  return(output_text)
}
```

```{r}
write_links <- function(yr_list) {
  glue("[{yr_list}](http://new.pmean.com/{yr_list}/)") %>%
    paste(collapse=" | ")
}
```

@@

```{r}
check_dates <- function(file_text) {
  file_text %>%
    str_subset("^date\\: ") %>%
    str_remove(fixed("date: ")) %>%
    str_remove_all('"') %>%
    str_remove_all("'")  -> file_date
  if (length(file_date)==0) return("Error: no date")
  if (length(file_date)>1) return("Error: multiple dates")
  return(file_date)
}
```

```{r}
write_list <- function(page_year) {
  # get file list
  list.files(path=glue("../text/{page_year}", pattern="*.md")) %>%
    str_subset("md$") -> f
  # open files and find information
  source_list <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{page_year}/{fn}"))
    # get source
    source_list <- append(
      source_list,
      check_source(file_text))
    #get dates
    date_list <- append(
      date_list,
      check_dates(file_text))
  }
  # strip extensions
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> f
  n <- length(f)
  # search for problem files
  bad_date <- str_detect(date_list, "Error")
  bad_source <- str_detect(source_list, "Error")
  # create RMarkdown text
  links <- glue(
    "+ {date_list} ",
    "[{f}]",
    "(http://new.pmean.com/{f}/)  ")
  # store in a sorted data frame
  o <- order(date_list, f)
  return(
    data.frame(
      f, 
      links,
      date_list,
      source_list,
      bad_date,
      bad_source)[o, ])
}
```

```{r}
for (four_digit_year in c("2022")) {
  two_digit_year <- str_sub(four_digit_year, 3, 4)
  yaml_text <- write_yaml(two_digit_year)
  l <- write_list(two_digit_year)
  n <- dim(l)[1]
  fn <- glue("../text/{two_digit_year}/{four_digit_year}.md")
  write_lines(
    yaml_text, 
    file=fn,
    append=FALSE)
  write_lines(
    glue("New website ({n} files)\n\n"),
    file=fn,
    append=TRUE)
  write_lines(
    l$links, 
    file=fn,
    append=TRUE)
  problem_files <- c(
    paste(l$f, l$date_list)[l$bad_date],
    paste(l$f, l$source_list)[l$bad_source])
  all_good <- "All files passed data and source quality checks"
  if (length(problem_files)==0) problem_files <- all_good
  write_lines(
    c("\n", problem_files),
    file=fn,
    append=TRUE)
}
```

Links created for `r dim(l)[1]` pages in `r four_digit_year`.

`r paste(problem_files, collapse="\n")`

`r l$source_list`

### 2023-01-12 text/21/cubic-splines.Rmd
Added source link to 2020 definition pages

---
title: "Basics of cubic spline models"
author: "Steve Simon"
date: "2021-11-01"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

>>>>

---
title: "Basics of cubic spline models"
source: new
author: "Steve Simon"
date: "2021-11-01"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

### 2023-01-12 text/21/venn-diagram.Rmd
Added source link to 2020 definition pages

---
title: "Test diagrams"
author: "Steve Simon"
source: "New"
date: "2021-10-30"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

>>>>

---
title: "Test diagrams"
author: "Steve Simon"
source: new
date: "2021-10-30"
categories:
- Blog post
tags:
- Graphical display
output: html_document
---

### 2023-01-12 text/21/very-simple-splines.Rmd
Added source link to 2020 definition pages

---
title: "Very simple spline models"
author: "Steve Simon"
date: "2021-10-29"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---

>>>>

---
title: "Very simple spline models"
source: new
author: "Steve Simon"
date: "2021-10-29"
categories:
- Recommendation
tags:
- Linear regression
output: html_document
---
